Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
Work on "Open problems"

\begin{itemize}
    \item
        In section~\ref{sec:reusable-specs}, we showed how to reuse
        pieces of specification.
    \item
        It would be possible and useful to write a library that
        provides reusable pieces of specification, for many of
        Haskell's standard classes.
        (similar in purpose to
        {\tt
        checkers}\footnote{http://hackage.haskell.org/package/checkers})
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Source locations for failing examples}

TBD:

We do not get source locations for failing tests. Doctest solves this.
Something like JHC's
\verb|SRCLOC_ANNOTATE|
pragma\footnote{%
http://repetae.net/computer/jhc/jhc.shtml} could help
for Hspec/QuickCheck/HUnit.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{TBD}

\begin{itemize}
    \item
        Feedback for failing QuickCheck properties is not always as
        useful as it could be -> combinators that use QuickCheck's
        Result type could help
    \item
\end{itemize}

>>>>

\begin{quote}
    TBD: A library for reusable pieces of specification would be
    useful.
\begin{itemize}
    \item
        In section~\ref{sec:reusable-specs}, we showed how to reuse
        pieces of specification.
    \item
        It would be possible and useful to write a library that
        provides reusable pieces of specification, for many of
        Haskell's standard classes.
        (similar in purpose to
        {\tt
        checkers}\footnote{http://hackage.haskell.org/package/checkers})
\end{itemize}
\end{quote}

When Hspec finds evidence that does not hold, it reports the
corresponding behavior to the developer.  It would be useful to
include the source file and location where the failing evidence is
defined, so that the developer can find it immediately.
Extending GHC with a mechanism similar to JHC's
\verb|SRCLOC_ANNOTATE| pragma\footnote{%
http://repetae.net/computer/jhc/jhc.shtml} would allow to solve this.

\begin{quote}
    sol: should we just remove the next paragraph?
\end{quote}

Feedback for failing QuickCheck properties is not always as useful as
it could be.
Combinators, similar to {\tt shouldBe}, that construct QuickCheck {\tt
Result}s could improve the situation.
